\subsection{UAV Toolbox}
The MATLAB UAV Toolbox for 3D simulation provides sophisticated visualization, precise flight path analysis, and interactive scenario design. Here are three of the reasons we utilized it:
\begin{itemize}
    \item
    Realistic and Interactive Experience: For studying PID control, the MATLAB UAV 3D simulation provides a realistic and interactive environment. We use simulation to examine the behavior of the UAV system rather than relying exclusively on theoretical concepts and mathematical equations. Experiment with different PID controller parameters to see how they affect the UAV's reaction and acquire hands-on experience tweaking the controller. This immersive learning experience aids in the integration of theory and practice.
    \item
    Efficient Parameter Tuning: For best performance, PID control frequently necessitates fine-tuning of the controller parameters. The UAV 3D simulation in MATLAB gives an easy way to experiment with different parameter values and see how they affect control performance. It enables us to iteratively tune the PID gains, simulate the system's response, and see how parameter changes impact stability, responsiveness, and robustness. This iterative tuning procedure helps us to get practical insights into the sensitivity of PID control to parameter changes, assisting in the development of intuition and skills in effectively tuning controllers.
    \item
    Analysis of Complex Scenarios: Control performance in complex circumstances can be analyzed using the MATLAB UAV 3D simulation. When numerous PIDs are involved, it can become difficult to intuitively understand how one effects another; thus, a visual representation aids in grasping and understanding the concepts.
\end{itemize}