\section{Wireless communication}
Drones are machines, which are able to go out of the connected cables' reach fast and easily, especially with flawed control algorithm. Therefore if mid-air communication is required, it is necessary to have wireless communication.

There are many options, but the ones used commonly for drones are primarily various forms of 2.4 GHz signals, as it provides the best middle ground between reach and speed. The 2.4 GHz has wide range of technologies supporting it, for example Bluetooth, Wi-Fi and various RF communication protocols. 

If a high performance drone was the goal, RF communication would be chosen, but for the purpose of this project Bluetooth or rather BLE is optimal, as the microchip has it inbuilt. BLE stands for Bluetooth low energy and is a separate technology of Bluetooth and requires different parts. BLE has lower power requirements, as it is primarily one way communication, where the packets are not being sent constantly, but only when needed or requested.

The implementation of BLE for nRF52840 in Arduino IDE usually relies on either Bluefruit LE or Adafruit BLE library, depending on whether pure C or Mbed is used, but they are similar in functions and procedures.

For a device to use BLE, it needs to be either peripheral, which advertises itself or central, which connects to the advertised peripheral. Peripheral has services, for example control service, which can have characteristics like state with 0 and 1 for turning on and off, X and Y with values from 0 to 1023 to control the direction.

This characteristic can have different options. Write: where the central writes to this characteristic, read: if central reads from it and notify: which lets the central know, that it has changed. Also a combination of these can define each characteristic.

In this case, the drone was chosen as a peripheral with characteristics mentioned above. To it, a controller with a joystick and two buttons connects as a central and writes to the characteristics. This was not used in the project, as the project did not reach stages requiring this.

The Kill switch turns the drone on and off in response to any communication received. It contains only one characteristic, which switches between 0 and 1 no matter what it receives which starts the drone on 1 and stops on 0. This would be controlled from a mobile phone for the sake of reliability. The option of sending gyro-data from a phone to the drone to mimic a controller was also explored, but required packet management, as the data packets sent were too long.

Last option which was explored was logging data through BLE. The challenging part is that BLE is aimed mainly at mobile devices and proprietary applications. Therefore there are no available applications for Windows which allow reading data from BLE devices and mobile phone applications do not offer the option of saving larger amounts of data. As a consequence of mentioned, data-logging through BLE was abandoned.